### 2024-06-24 manuscript.tex
Add a figure with AVBC example
Add photos to the map figure

\begin{figure}
\centering
\includegraphics[width=0.65\textwidth]{img/map.png}
\caption{
A map showing the tracks of 31 voyages of RV \emph{Polarstern}, RSV
\emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B. Palmer}, and
HMNZS \emph{Wellington} and one sub-Antarctic station (Macquarie Island)
analysed here. The tracks cover Antarctic sectors south of South America, the
Atlantic Ocean, Africa, Australia, and New Zealand in the years 2010 to 2021.
The dashed line at 40$^\circ$S delineates the Southern Ocean area of our
analysis.
}
\label{fig:map}
\end{figure}

@@

Together, we analysed data from 31 voyages of RV \emph{Polarstern}, RSV
\emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B. Palmer}, Her
Majesty's New Zealand Ship (HMNZS) \emph{Wellington} and one sub-Antarctic
station (Macquarie Island) in the SO south of 40°S between year 2010 and 2021
(Fig. \ref{fig:map} and Table \ref{tab:voyages}). Altogether, the voyages and
the station comprised 2421 days of data south of 40$^\circ$S, but the
availability of ceilometer data was smaller.

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/map-fig.png}
\caption{
\textbf{(a)} A map showing the tracks of 31 voyages of RV \emph{Polarstern}, RSV
\emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B. Palmer}, and
HMNZS \emph{Wellington} and one sub-Antarctic station (Macquarie Island)
analysed here. The tracks cover Antarctic sectors south of South America, the
Atlantic Ocean, Africa, Australia, and New Zealand in the years 2010 to 2021.
The dashed line at 40$^\circ$S delineates the Southern Ocean area of our
analysis. A photo of \textbf{(b)} RV \emph{Polarstern} (© Folke
Mehrtens/Alfred-Wegener-Institut), \textbf{(c)} Lufft CHM 15k installed on RV
\emph{Tangaroa} (© Peter Kuma), \textbf{(d)} Vaisala CL51 install at the
Macquarie Island station (© Jeﬀ Aquilina, Bureau of Meteorology).
% TODO: Ask for photo permission and info about license.
}
\label{fig:map}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/example.png}
\caption{
An example of attenuated volume backscattering coefficient (AVBC) measured by
CL51 during 24 hours on the PS81/3 voyage and an equivalent AVBC simulated with
the ALCF from ERA5 data during the same time period. Shown is also the cloud
mask determined by the ALCF.
}
\label{fig:example}
\end{figure}

@@

Together, we analysed data from 31 voyages of RV \emph{Polarstern}, resupply
vessel (RSV) \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B.
Palmer}, Her Majesty's New Zealand Ship (HMNZS) \emph{Wellington} and one
sub-Antarctic station (Macquarie Island) in the SO south of 40°S between year
2010 and 2021 (Fig. \ref{fig:map} and Table \ref{tab:voyages}). Altogether, the
voyages and the station comprised 2421 days of data south of 40$^\circ$S, but
the availability of ceilometer data was smaller.
